---
title: "p8105_hw5_nz2333"
author: "nz2333"
date: "11/20/2021"
output: github_document
---

```{r}
library(tidyverse)
library(tidyr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1
```{r message = FALSE}
data_p1 = read_csv(url("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"))
```

The datset has 52179 observations and 12 variables. It provides information on reported homicides in the U.S., with victims' names, race, age, sex, reported date, location: city, state, longitude, and latitude; and disposition. 

_City_state, Homicides number, Unsolved number_
```{r}
data_p1  = data_p1 %>%
  mutate(
    city_state = paste(city, state, sep = ", ")
  )

homicides = data_p1 %>%
  group_by(city_state) %>%
  summarize(homicides = n())

unsolved = data_p1 %>%
  filter(disposition %in% c("Closed without arrest", "Open/No arrest")) %>%
  group_by(city_state) %>%
  summarize(unsolved = n())

summary = left_join(homicides, unsolved, by = "city_state")

knitr::kable(summary)
```

```{r}
Baltimore = summary %>%
  filter(city_state == "Baltimore, MD")

result = prop.test(Baltimore %>% pull(unsolved), Baltimore %>% pull(homicides)) %>%
  broom::tidy()

result
```

```{r}
test = function(summary) {
  test_result = prop.test(
    summary %>% pull(unsolved), summary %>% pull(homicides)) %>%
    broom::tidy() 
    tibble(
      proportion = test_result %>% pull(estimate), 
      lowCI = test_result %>% pull(conf.low), 
      highCI = test_result %>% pull(conf.high)
    )

}

test(Baltimore)

```


## Problem 2
```{r}
df_p2 = tibble(
  file = list.files(
  "./data"))

read_data = function(name) {
  read_csv(str_c("./data/", name))
}

df_p2 = df_p2 %>%
  mutate(data = map(file, read_data)) %>%
  unnest(data)

final_data = df_p2 %>%
  mutate(file = str_replace(file, ".csv", "")) %>%
  separate(file, into = c("Arm", "ID"), sep = "_", remove = FALSE)
```

_Spaghetti plot_
```{r}
plot = final_data %>%
  pivot_longer(week_1:week_8, 
               names_to = "Week", 
               values_to = "Obs") %>%
  ggplot(aes(x = Week, y = Obs, group = file, color = Arm)) +
  geom_line() +
  labs(x = "Week", 
       y = "Observations on each subject",
       title = "Observations on each subject over time")

plot
```

The observations are similar at the beginning. The control arm fluctuated but show a steady trend over time. The experimental arms show positive slopes that the observations are increasing over time. 

## Problem 3
```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

```{r}
fill_nas = function(var) {
  if (is.numeric(var)) {
    var[is.na(var)] = mean(var, na.rm = TRUE)
  }
  else if (!is.numeric(var)) {
    var[is.na(var)] = "virginica"
  }
  return(var)
}
```

```{r}
map(iris_with_missing, fill_nas)
```


